DecentraliDrone: A Decentralized, Fully Autonomous Drone Delivery System for Reliable, Efficient Transport of Goods

### 2023-12-11 paper.tex
re: cited and added eqns
update: paper revision v_1

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}

\title{DecentraliDrone: A Decentralized, Fully Autonomous Drone Delivery System for Reliable, Efficient Transport of Goods}
\author{Abdul Aziz A.B, Dhairya Gupta, Samik Saraswat}
\date{January 1, 2023}

@@

\maketitle

\begin{abstract}
DecentraliDrone is a innovative drone delivery system that utilizes advanced technology to transport goods efficiently and reliably. Our system is fully autonomous and decentralized, meaning that it operates without the need for human intervention and relies on a distributed network of drones and devices to function. In this paper, we describe the architecture and key features of DecentraliDrone, and discuss the challenges and potential applications of this system.
\end{abstract}

@@

There are also potential regulatory and environmental challenges to be considered in the development of decentralized autonomous drone delivery systems. DecentraliDrone addresses these issues by following all relevant regulations and utilizing energy-efficient drones and devices that minimize their environmental impact.

In conclusion, DecentraliDrone is a revolutionary drone delivery system that utilizes advanced technology to transport goods efficiently and reliably. The fully autonomous and decentralized nature of the system ensures that it is able to operate without the need for human intervention and can continue to make deliveries even in the event of technical issues. By addressing the key challenges of ensuring the safety and reliability of the drones, integrating them into existing logistics and delivery systems, and addressing potential regulatory and environmental issues DecentraliDrone is well-positioned to revolutionize the way we transport goods. In the future, we envision a world where DecentraliDrone is widely used for a variety of delivery applications, including same-day delivery of packages and groceries, transportation of medical supplies and equipment, and emergency response deliveries.

Furthermore, the decentralized nature of DecentraliDrone allows it to operate in a wide range of environments, including urban, rural, and remote areas. This makes it a versatile delivery solution that can meet the needs of a wide range of users.

In addition to its practical applications, DecentraliDrone has the potential to have a positive impact on society. By reducing the need for human operators and traditional delivery methods, DecentraliDrone can help to reduce traffic congestion, air pollution, and other environmental issues associated with transportation.

Overall, DecentraliDrone is a promising technology that has the potential to revolutionize the way we transport goods and make a positive impact on society. We look forward to continuing to develop and improve upon this technology in the future.

@@

There have been several previous works on decentralized autonomous drone delivery systems. Li et al. \cite{li2018review} review various key technologies and applications of decentralized autonomous drone delivery systems, including routing algorithms, communication protocols, and collision avoidance systems. Zhou et al. \cite{zhou2018routing} review routing algorithms and communication protocols used in decentralized autonomous drone delivery systems. Wang et al. \cite{wang2018survey} provide an extensive survey of decentralized autonomous drone delivery systems, covering design approaches, applications, and challenges.

>>>>

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references

\documentclass[preprint,12pt]{elsarticle}
\usepackage{graphicx}
%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
\usepackage{epsfig}
\usepackage{longtable}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{subcaption}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Alexandria Engineering Journal}

@@

\begin{frontmatter}

\title{DecentraliDrone: A Decentralized, Fully Autonomous Drone Delivery System for Reliable, Efficient Transport of Goods}

\author[a]{A Sheik Abdullah\corref{cor1}}
\ead{sheik.abdullah@vit.ac.in}

\author[a]{Abdul Aziz A.B}
\ead{abdulaziz.ahamed2020@vitstudent.ac.in}

\author[a]{S.Geetha\corref{cor1}}
\ead{s.geetha@vit.ac.in}

\cortext[cor1]{Corresponding author(s)}

\address[a]{School of Computer Science and Engineering, Vellore Institute of Technology - Chennai Campus, Chennai 600127, Tamil Nadu, India}

\begin{abstract}
As the world becomes more interconnected and globalized, the demand for efficient and reliable delivery systems is on the rise. To meet this demand, we propose DecentraliDrone, an innovative drone delivery system that utilizes advanced technology to transport goods autonomously and efficiently. Our system is fully decentralized, meaning that it operates without the need for human intervention and relies on a distributed network of drones and devices to function. One of the key features of DecentraliDrone is its autonomy. The system operates without the need for human intervention, enabling it to operate 24/7 and reducing the risk of accidents caused by human error. Additionally, our system is highly scalable, allowing it to adapt to changing demands and expand its delivery capabilities.
There are several challenges that must be addressed in order to fully realize the potential of DecentraliDrone. These include developing robust communication protocols, ensuring the safety and security of the system, and addressing regulatory and legal issues related to autonomous delivery systems.

\end{abstract}\\

%%Graphical abstract
\begin{graphicalabstract}
\includegraphics[width=16cm]{grabs}
\end{graphicalabstract}
%%Research highlights
\begin{highlights}
\item The system ensures faster, accurate deliveries by eliminating human-operated constraints.

\item Real-time routing optimization enhances delivery efficiency, adapting to changing conditions seamlessly.

\item Utilizes Advanced Algorithms for Real-time Danger Detection and Collaborative Decision-making.

\item The system complies with regulations, integrates safety protocols, and prioritizes energy-efficient, environmentally friendly operations.

\item Hybrid drone system that has a greater flight time by using both fuel as well as electric cells.

\end{highlights}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Reinforcement Learning \sep OpenCV \sep Unreal Engine \sep Swarm \sep MetaShape \sep V-SLAM \sep Autonomous System \sep Decentralization
%% PACS codes here, in the form: \PACS code \sep code
\PACS 42.30.Va \sep 07.05.Mh 
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\MSC 68T05 \sep 68T40 \sep 68T45 \sep 68U20
\end{keyword}

\end{frontmatter}

@@

There are also potential regulatory and environmental challenges to be considered in the development of decentralized autonomous drone delivery systems. DecentraliDrone addresses these issues by following all relevant regulations and utilizing energy-efficient drones and devices that minimize their environmental impact, the decentralized nature of DecentraliDrone allows it to operate in a wide range of environments, including urban, rural, and remote areas. This makes it a versatile delivery solution that can meet the needs of a wide range of users.

We believe this is a promising technology that has the potential to revolutionize the way we transport goods and make a positive impact on society. We look forward to continuing to develop and improve upon this technology in the future.

\section{Components of the System}\\

DecentraliDrones comprises of various essential components, each playing a distinct role in ensuring the successful and efficient delivery of packages. These components are grouped into several key categories, with specific functionalities and tasks assigned to each. The system operates cohesively, combining the efforts of multiple groups to achieve seamless package delivery.

\begin{enumerate}
\item \textbf{Drone Fleet:}
\begin{itemize}
  \item \textbf{Drone Operations Group:}
    \begin{itemize}
      \item Responsible for managing the entire drone fleet.
      \item Monitors drone health and coordinates maintenance activities.
      \item Ensures drones are adequately charged and prepared for deliveries.
    \end{itemize}
  \item \textbf{Drone Routing and Scheduling Group:}
    \begin{itemize}
      \item Develops optimized delivery routes based on package destinations.
      \item Schedules delivery times for maximum efficiency.
      \item Considers factors like weather conditions, traffic, and delivery priorities.
    \end{itemize}
\end{itemize}

\item \textbf{Package Handling:}
\begin{itemize}
  \item \textbf{Loading and Unloading Group:}
    \begin{itemize}
      \item Handles the loading and unloading of packages onto drones.
      \item Ensures secure attachment and proper balancing.
      \item Coordinates with the Drone Operations Group for timely departures.
    \end{itemize}
  \item \textbf{Package Sorting and Categorization Group:}
    \begin{itemize}
      \item Sorts packages based on size, weight, and destination.
      \item Categorizes packages for efficient loading and route planning.
      \item Coordinates with the Drone Routing and Scheduling Group for optimized load distribution.
    \end{itemize}
\end{itemize}

\item \textbf{Navigation and Safety:}
\begin{itemize}
  \item \textbf{Navigation and Guidance Group:}
    \begin{itemize}
      \item Develops and maintains navigation algorithms for drones.
      \item Ensures accurate positioning and obstacle avoidance.
      \item Collaborates with the Drone Routing and Scheduling Group to follow designated routes.
    \end{itemize}
  \item \textbf{Safety and Compliance Group:}
    \begin{itemize}
      \item Monitors regulatory compliance and airspace regulations.
      \item Implements safety protocols to handle emergencies.
      \item Coordinates with local authorities and air traffic control for airspace access.
    \end{itemize}
\end{itemize}

\end{enumerate}\\

These components work together harmoniously to establish a fully functional Drone Delivery System, effectively harnessing the capabilities of autonomous aerial vehicles to transform the delivery industry.

@@

The research on Simultaneous Localization and Mapping (SLAM) has primarily concentrated on centralized multi-robot systems, which yield precise maps but exhibit constraints in scalability, adaptability to environmental changes, and resilience in hostile conditions. In response, Swarm SLAM has emerged as a promising solution, facilitating the creation of decentralized, scalable, adaptable, and fault-tolerant maps. While Swarm SLAM holds great potential, its adoption faces significant technological and financial challenges, yet it proves valuable in scenarios with time or cost constraints and in dynamic environment monitoring. This paper explores potential applications of Swarm SLAM and the associated obstacles, emphasizing the need for suitable, distributed data exchange strategies\cite{li2018review}.

In both research and education, there is a growing focus on visual-SLAM (v-SLAM) and Unmanned Aerial Vehicle (UAV) navigation. However, physical testing poses challenges due to safety restrictions, battery limitations, and complex hardware setups. To address these constraints, custom simulators have been developed that incorporate localization, mapping, and path-planning modules, providing effective platforms for the development of navigation algorithms and autonomous systems\cite{zhou2018routing}.

Further, a comprehensive survey bridges SLAM and data fusion in UAVs, with a focus on multi-sensor fusion. The authors discuss various SLAM techniques, such as Kalman filters, extended Kalman filters, and their role in UAV scene perception, mapping, and localization\cite{wang2018survey}. Data fusion stands as a crucial aspect of SLAM, although it encounters challenges such as uncertain data, noise, and reliability\cite{kegeleirs2021swarm}.

A novel estimation method is proposed for UAVs, employing an Extended Kalman Filter and data fusion from multiple sensors, including a monocular camera. This method enhances trajectory estimation and overcomes issues in metric scale recovery. The integration of visual data from a downward-facing camera enhances its capabilities\cite{chen2022end}.\\ Additionally, a SLAM system designed for low-cost commercial aerial platforms with limited onboard computing capacity is introduced. It combines data from a monocular camera, Inertial Measurement Unit (IMU), and altimeter to calculate the platform's pose and environment map. Designed for low-cost aerial platforms, this SLAM system makes intentional use of low-cost sensors\cite{gupta2022slam}.

In the domain of multi-UAV systems, a framework for cooperative SLAM-based exploration with limited communication bandwidth is proposed. The RGB-D based grid mapping system enhances exploration by optimizing the flight paths of multiple UAVs and reducing memory consumption by sharing only the necessary data\cite{munguía2016vslam}. The decentralization of SLAM is a significant focus, leading to the development of the SLAM algorithm. It demonstrates high-precision local localization capability and real-time high-precision relative localization when UAVs are in proximity\cite{lópez2017sensorial}.\\
An innovative hybrid multirotor drone architecture that employs gasoline engines in addition to electric motors for propulsion is presented. This hybrid system offers longer flight times and reduced energy consumption, benefiting various applications such as package delivery\cite{stolaroff2018energy}. The transition to drone-based delivery systems has the potential to reduce greenhouse gas emissions in the freight sector. Drone delivery systems demonstrate advantages over traditional ground vehicle delivery methods, with higher energy efficiency and lower emissions\cite{jarrah2022flight}.
Loop closure detection in SLAM systems is an essential process to improve mapping and localization accuracy. Deep learning-based techniques have been applied for loop closure detection in both visual and LiDAR SLAM, presenting a promising direction for improving SLAM systems\cite{arshad2021loop}. An advanced path planning method for autonomous heterogeneous UAVs is explored, which is essential for efficient coverage in various scenarios. The use of mixed-integer linear programming and clustering-based algorithms optimizes the flight paths of UAVs for accurate and effective coverage\cite{chen2022coverage}.\\
Path planning and obstacle avoidance are critical for autonomous vehicles. The research introduces a technique that combines path pruning, smoothing, and optimization, along with geometric collision detection. While the experiments are conducted in static environments, real-world scenarios may require dynamic obstacle detection\cite{yang2021rrt}. SLAM solutions have evolved towards incorporating both visual and LiDAR data for improved performance. However, more research is needed to develop tightly coupled LiDAR-vision sensor fusion algorithms\cite{debeunne2020vlidar}. Path planning is crucial for autonomous navigation. This paper offers an overview of various path planning algorithms for different types of robotic systems, serving as a valuable resource for those looking to implement autonomous navigation\cite{karur2021path}.\\
Swarm intelligence has gained attention, particularly in swarm robotics and drone systems. Communication strategies are critical, taking into account factors such as energy consumption, range, and latency for ad hoc mesh networks, especially when used in swarm networks\cite{cui2017brief}.\\ Swarm robotics presents challenges and opportunities in fire-fighting scenarios. The research focuses on the self-organization of swarms of firefighting drones, utilizing Particle Swarm Algorithms for improved performance in dynamic environments\cite{innocente2019self}. The paper introduces a dynamic optimization problem related to Unmanned Aerial Vehicle (UAV) search and rescue scenarios, known as the Moving Peak Drone Search Problem (MPDSP). A solution is proposed to maximize the effectiveness of a UAV fleet searching a large area\cite{kyriakakis2021moving}. A decentralized omnidirectional visual-inertial-UWB state estimation for aerial swarms, offers insights into robust swarm navigation and state estimation\cite{xu2022omni}.\\

\section{Schematics of the Proposed System}\\

In the context of the system, we have two primary end users, each with distinct roles and responsibilities.

\subsection{Customer Perspective:}
\begin{enumerate}
\item Place an order within the mobile app.
\item Acquire and place a unique ArUco marker code.
\item Request autonomous delivery.
\item Verify and accept the delivery upon marker recognition.
\end{enumerate}

\subsection{Recipient Perspective:}
\begin{enumerate}
\item Prepare to receive a drone delivery.
\item Place the ArUco marker on a suitable surface.
\item Verify and accept the delivery upon marker recognition.
\item If needed, respond to incomplete delivery alerts for resolution.
\end{enumerate}

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=9cm, height=7cm]{images/td3_algo.png}
    \caption{DecentraliDrones Methodology Network}
\end{figure}\\
For the Critic network, the loss function is expressed as:
\begin{equation}
\label{eq:first}
J(\theta_i) = N^{-1}\sum(y - Q_{\theta_i}(S,a))^2
\end{equation}

where:\\
\begin{align*}
&J(\theta_i) \text{ - Critic loss.} \\
&N \text{ - Batch size.} \\
&y \text{ - Target value.} \\
&Q_{\theta_i}(S,a) \text{ - Estimated Q-value.} \\
\end{align*}

For actor networks, a deterministic strategy is used to optimize the parameters, and the loss function is expressed as:
\begin{equation}
\label{eq:second}
{\nabla_\phi}{J(\phi)}=N^{-1}\sum\nabla_{a}Q_{\theta_i}(s,a)|_{a=\Pi_{\phi(s)}}\nabla_{\phi}\Phi_\phi(s)
\end{equation}

where:\\
\begin{align*}
&\nabla_\phi J(\phi) \text{ - Actor loss gradient.} \\
&N \text{ - Batch size.} \\
&Q_{\theta_i}(s,a) \text{ - Estimated Q-value.} \\
&\Pi_\phi(s) \text{ - Deterministic policy.} \\
&\nabla_\phi\Phi_\phi(s) \text{ - Policy gradient.} \\
\end{align*}

Time and Space Complexity Associated with TD3-
The time and space complexity of the TD3 algorithm depend on several factors such as the size of the state and action spaces, the number of layers and neurons in the neural networks, the batch size used for updates, and the length of the training process. 
Overall, the time and space complexity of the TD3 algorithm depend heavily on the size of the neural networks and the batch size used for updates. As these can be adjusted based on the available computational resources, it is difficult to give a general estimate of the complexity of the algorithm. However, it is safe to say that TD3 can be computationally expensive to train, especially for large state and action spaces. \\

\subsection{Basic Architecture Flowchart}\\

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=8.5cm, height=8cm]{images/architecture_new.png}
    \caption{Architecture Flowchart}
\end{figure}

The customer will raise the request for the purchase and delivery of a specific item through the app interface. The app interface consists of Destination details of the customer, progress updates of the delivery and the payload specifications, i.e., the order details in terms of weight, dimensions and other attributes. The delivery recipient will acquire a unique ArUco marker code mapped to the unique delivery. The recipient has to find a suitable flat surface and place the marker code at the respective position after printing it. Each unique delivery will be mapped to a pair of drones within the drone swarm. The delivery vicinity details will be given as input to the drone unit for the implementation of autonomous delivery.\\
With the help of Path planning algorithms such as TD3 the drone unit will navigate towards the destination vicinity autonomously. These algorithms will ensure the obstacle avoidance, course correction and smooth and effective path planning for reaching the destination. A pair of drone will be assigned to each delivery to ensure smoothness in the delivery as 1 drone will carry the payload and implement V-SLAM while other drone will be giving visual aide and extending the vision of the first drone. This data helps in course correction and precise and accurate navigation to the destination vicinity. Once the drone unit reaches the destination vicinity. After reaching the destination vicinity, the drone unit pair would lower the altitude and start searching for the ArUco marker in the compound using openCV component. If the marker is found and matched by the drone unit, then the drone unit would complete the delivery. After completing the delivery, it would update in the app interface and the logger about the progress and return back to drone dispatch spawn unit. \\
In case the marker is not found or found in an unsuitable environment for completing the delivery, the drone unit would raise a request/alert in the app interface. The recipient will have to respond within a time limit and fix the placement of ArUco, if these conditions are met then the raised request is accepted and the drone unit can proceed with the delivery procedure. If the recipient fails to respond to the request within the specific time-frame, the drone unit would return back to the drone dispatch spawn unit and log that scenario as an incomplete delivery.

\subsection{Swarm Schematics}
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=8.5cm, height=9cm]{images/Decentralized_Structure.png}
    \caption{Decentralized Swarm Structure of Drone Network}
\end{figure}

This schematic explains the basic workings behind the communications involved among the swarm of drones that are deployed, being a decentralised system, they check in on each other for the delivery states and carry out the delivery screening process where they travel around the delivery point and drop the packages where and when required. The drones also keep track of the individual check ins so that when one of the drones faults to an unfortunate circumstance, the system balances itself by sending in a replacement by peer communication via the group check in feature.\\

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=8cm, height=8cm]{images/communication_schematics.png}
    \caption{Drone Activity Diagram}
\end{figure}

The following diagram gives a sharp overview of the communication that occurs among the drones to make successful deliveries, being in a decentralised system, the drones are their own controller entity as a whole system, the success of the system is considered as a group effort rather than a singular entity’s success, keeping this in mind, the drones communicate with each other to make sure that the deliveries are made. The communication is done through cellular towers present across the region where the drones are deployed for delivering the goods.\\

\subsection{Functional Quad-rotor Schematics}\\

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=8.5cm, height=6.5cm]{images/quad-rotor_schematics.png}
    \caption{Single Drone Schematic Diagram}
\end{figure}

The following diagram explains the functioning of a singular entity from the system of swarm. Each quad-rotor entity has its own guidance system that is line of sight based, acting upon which the motors and propellers are instructed to take the ascend or descend of the drone, it uses computer vision algorithms to perform obstacle detection and avoidance, the guidance system gives the appropriate trajectory for the drone to take in order to make a successful delivery happen in accordance to the environmental factors that are laid upon in its path. The Guidance system takes the inputs from the navigation system and performs the appropriate logical decisions to map out the path for the drone.\\

\subsection{Takeoff and Landing for VTOL Schematics}\\
The illustrated diagram provides a comprehensive depiction of the intricate takeoff and landing sequence of the drone. Notably, the drone is strategically designed to land precisely on specified markers during each delivery. This precision landing mechanism is a fundamental component of the overall system, ensuring that the drone consistently lands and takes off at predetermined locations.

The underlying technology facilitating this process is a Vertical Takeoff and Landing (VTOL) system, which incorporates sophisticated altitude and position control. This system plays a pivotal role in orchestrating the drone's movements, allowing it to navigate with precision and accuracy during both takeoff and landing phases.

To further enhance operational efficiency and safety, the drone is equipped with fall detection systems. These systems serve a crucial function by promptly detecting any instances of unplanned descents or falls. In the event of such incidents, the fall detection systems generate alerts, notifying other drones within the swarm. These alerts serve a dual purpose – not only do they signal the need for immediate maintenance for the affected drone, but they also communicate the status of an incomplete delivery. Subsequently, neighboring drones in the vicinity can make informed decisions about whether to take charge of the pending delivery or provide support for maintenance activities.

This integrated approach to precision landing and fall detection underscores the advanced capabilities of the drone system, emphasizing its commitment to operational reliability, safety, and collaborative decision-making within the drone swarm.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=7.0cm, height=5.5cm]{images/takeoff_landing.png}
    \caption{Takeoff and Landing Pre-flight Schematics for Single Drone}
\end{figure}

\begin{table}[htbp]
  \centering
  \caption{Multicopter Specifications}
  \begin{tabular}{lcccc}
    \toprule
    Model & Airframe Mass (kg) & Total (kg) & Flight Time (min) & Takeoff (kg) \\
    \midrule
    DJI Matrice 600 & 5.96 & 9.5 & 32 & 15.1 \\
    DJI M200 & 2.76 & 3.80 & 27 & 6.1 \\
    Kitty Hawk & 4.08 & 9.15 & 30 & 18.6 \\
    \bottomrule
  \end{tabular}
\end{table}\\

\begin{table}[htbp]
  \centering
  \caption{HES Aerostak Fuel Cell Specifications}
  \begin{tabular}{lccccc}
    \toprule
    Power (W) & Mass (kg) & L/min & Pressure (bar) & Equivalent Volume (L) & Time (s) \\
    \midrule
    200 & 2.06 & 2.8 & 0.5 & 1200 & 25714 \\
    500 & 2.90 & 6.5 & 0.5 & 1200 & 11077 \\
    1000 & 3.75 & 14 & 0.55 & 1091 & 4675 \\
    \bottomrule
  \end{tabular}
\end{table}\\

The energy efficiency of a drone can be calculated as the ratio of useful work (such as lifting a payload or performing a task) to the energy input (typically from the battery):
\begin{equation}
\text{Energy Efficiency (\%)} = \frac{\text{Useful Work}}{\text{Energy Input}} \times 100
\end{equation}

The flight time of a drone can be estimated using the following equation:
\begin{equation}
\text{Flight Time (minutes)} = \frac{\text{Battery Capacity (Wh)}}{\text{Power Consumption (W)}}
\end{equation}
Where:
Battery Capacity (Wh) is the capacity of the drone's battery in watt-hours.
Power Consumption (W) is the average power consumption of the drone during flight.
It's important to note that power consumption varies based on factors such as drone weight, motor efficiency, aerodynamics, and flight conditions.

The endurance of a drone refers to how long it can stay in the air under specific conditions. It can be calculated using a similar equation to flight time:
\begin{equation}
\text{Endurance (minutes)} = \frac{\text{Battery Capacity (Wh)}}{\text{Power Consumption (W)}}
\end{equation}
The endurance equation is particularly useful when optimizing drones for specific missions or tasks where extended flight time is essential.

The energy consumption rate of a drone can be expressed as:
\begin{equation}
\text{Consumption Rate (Wh/min)} = \frac{\text{Battery Capacity (Wh)}}{\text{Flight Time (min)}}
\end{equation}
This equation helps you understand how quickly a drone consumes its battery energy during flight.

Table 2  underscores the fuel cell's efficiency by revealing its ability to deliver significant power output (200 W to 1000 W) while consuming relatively small amounts of hydrogen (2.8 L/min to 14 L/min). These specifications demonstrate its suitability for applications where both power and fuel efficiency are crucial, making it an environmentally friendly and cost-effective choice for energy generation.

\subsection{App Schematics}\\

\begin{figure}[!htbp]
    \vspace{-2.5cm}
    \centering
    \includegraphics[width=7.0cm, height=5.5cm]{images/app_schematics.png}
    \caption{Drone Delivery Application Schematics}
\end{figure}

This diagram explains the workings that are underlying in the application that is developed specifically for this system to be achieved, it explains the confirmation of the buyer to whom the goods are delivered and the unique ArUco markers that are generated for each deliveries, the items involved in the delivery, the locations to be delivered and so on.
\section{CAD Model of the Hybrid Drone}

In this section, we delve into the CAD model of the Hybrid drone, providing insights into its design, components, and specifications.

\subsection{CAD Model Description}

\begin{enumerate}
    \item \textbf{Drone Configuration:} The hybrid drone is designed in the Quad(X) Configuration, which provides stability and maneuverability.

    \begin{figure}[!htbp]
    \centering
    \includegraphics[width=8cm, height=4cm]{images/X_config.png}
    \caption{Drone in X Config}
    \end{figure}

    \item \textbf{Hybrid Power-Based Design:} The drone features a hybrid power-based design, combining four electric motors with two petrol engines to optimize energy consumption and flight time.

    \begin{figure}[!htbp]
    \vspace{-3.5cm}
    \centering
    \includegraphics[width=8cm, height=4cm]{images/config2.png}
    \caption{Hybrid Model}
    \end{figure}

    \item \textbf{Protective Dome:} A synthetic dome covers the brain of the drone, housing sensitive sensors, flight controllers, and microcontrollers. It safeguards critical components.

    \begin{figure}[!htbp]
    \centering
    \includegraphics[width=6cm, height=3cm]{images/dome.png}
    \caption{Protective Dome of Drone}
    \end{figure}

    \item \textbf{Hybrid Power Source:} The drone is equipped with a fuel tank serving as a hybrid power source, ensuring extended flight duration.\\

    \begin{figure}[!htbp]
    \centering
    \vspace{-7mm}
    \includegraphics[width=8cm, height=4cm]{images/fuel_tank.png}
    \caption{Side View of Fuel Tank}
    \end{figure}

    \begin{figure}[!htbp]
    \centering
    \vspace{-1cm}
    \includegraphics[width=8cm, height=4cm]{images/fuel_tank2.png}
    \caption{Bottom View of Fuel Tank}
    \end{figure}

    \item \textbf{Manipulator Component:} The drone is equipped with tentacular manipulators designed to handle associated payloads effectively.

    \begin{figure}[!htbp]
    \centering

    \includegraphics[width=8cm, height=4cm]{images/manipulator.png}
    \caption{Drone Tentacular Manipulators}
    \end{figure}
\end{enumerate}

\subsection{Proposed Framework and Architecture}
The drone's architecture follows a decentralized approach, enabling it to work autonomously and collaboratively within a swarm. The framework incorporates various communication protocols, algorithms for path planning, and optimization techniques.

\subsubsection{Protocols}
Communication among the drone swarm is facilitated through custom protocols designed to ensure seamless coordination.

\subsubsection{Path Planning and Optimization Algorithms}
The drone employs sophisticated path planning algorithms, such as TD3, for obstacle avoidance, course correction, and efficient navigation. Optimization algorithms are integrated to enhance energy efficiency and route selection.

\subsection{Computer Vision-Based Components}
The drone leverages computer vision algorithms for tasks like object detection, marker recognition, and visual navigation. This includes Visual SLAM and other relevant techniques.

\subsection{CAD Design and Specifications}
The CAD design incorporates specific dimensions, materials, and structural details. Specifications include payload capacity, flight range, and more.

\begin{table}[!htbp]
\centering
\caption{Specifications and Values}
\begin{tabular}{|l|l|}
\hline
Specification       & Value             \\
\hline
Payload Capacity    & 20 kg             \\
Flight Range        & 200 km            \\
Battery Capacity    & 25,000 mAh        \\
Maximum Speed       & 100 km/h          \\
Fuel Tank Capacity   & 10 liters         \\
\hline
\end{tabular}
\end{table}

\subsection{Formulas and Equations}

\begin{equation}
\text{Energy Consumption} = \frac{\text{Fuel Consumed}}{\text{Flight Distance}}
\end{equation}
For calculating the energy consumption of the hybrid drone by dividing the amount of fuel consumed by the distance traveled during the flight.

\begin{equation}
\text{Optimization Objective} = \sum_{i=1}^{n} C_i x_i
\end{equation}
To represent an optimization objective where \(\sum_{i=1}^{n}\) indicates the sum of all \(n\) optimization factors (e.g., energy efficiency, path length) weighted by their respective coefficients \(C_i\).

\begin{equation}
\text{Path Length} = \int_{t_0}^{t_1} \sqrt{(dx/dt)^2 + (dy/dt)^2} dt
\end{equation}
Was used to compute the path length during a drone's flight by integrating the Euclidean distance over time, where \(dx/dt\) and \(dy/dt\) are the rate of change of the drone's position in the x and y directions.

\begin{equation}
\text{Marker Recognition Accuracy} = \frac{\text{Correct Matches}}{\text{Total Matches}}
\end{equation}
For measuring the marker recognition accuracy, which is the ratio of correctly recognized markers to the total number of matched markers.

\begin{equation}
\text{Fuel Efficiency} = \frac{\text{Flight Distance}}{\text{Fuel Consumed}}
\end{equation}
The formula calculates the fuel efficiency of the drone by dividing the flight distance by the amount of fuel consumed.

\begin{equation}
\text{Time to Destination} = \frac{\text{Distance}}{\text{Speed}}
\end{equation}
Computes the estimated time required to reach the destination based on the distance to be covered and the drone's speed.

\begin{equation}
\text{Takeoff Thrust} = \text{Weight} + \text{Lift Force}
\end{equation}
Takeoff thrust is determined by adding the weight of the drone to the required lift force to overcome gravity.

\begin{equation}
\text{Landing Approach Angle} = \tan^{-1}\left(\frac{\text{Vertical Descent Rate}}{\text{Horizontal Approach Speed}}\right)
\end{equation}
Calculates the landing approach angle, which is the angle at which the drone descends during the landing phase.

\begin{equation}
\text{Aerodynamic Lift} = \frac{1}{2} \times \text{Air Density} \times \text{Aerodynamic Coefficient} \times \text{Wing Area} \times \text{Velocity}^2
\end{equation}
The aerodynamic lift force acting on the drone's wings, considering factors such as air density, aerodynamic coefficient, wing area, and velocity.

\begin{equation}
\text{Drag Force} = \frac{1}{2} \times \text{Air Density} \times \text{Drag Coefficient} \times \text{Frontal Area} \times \text{Velocity}^2
\end{equation}
The drag force experienced by the drone, considering air density, drag coefficient, frontal area, and velocity.

\section{Result Comparison of Existing and Our System}
\textit{A Brief Overview of Parameters}\\

\subsubsection{Best Y}\\
The \textit{"best Y vs episode" }graph shows the maximum reward achieved by the agent in each episode during training. The graph is useful for evaluating the overall performance of the agent during training. The graph shows a steady increase in the maximum reward achieved over the course of training, indicating that the agent is improving its performance.\\

In the early episodes of training, the maximum reward achieved may be low but as it progresses, the maximum reward achieved should increase as the agent becomes more skilled at selecting actions that lead to higher rewards.
The shape of the graph can vary depending on the specific environment and hyperparameters used for training. However, in general, it should show a positive trend over time. If the graph shows a plateau or a decline in the maximum reward achieved, it may indicate a problem with the training process or the environment. \\

\subsubsection{Actor loss}\\
The graph of \textit{“Actor loss vs episodes” } shows how the loss of the actor changing over the course of training. The actor loss is a measure of how well the actor can select actions that lead to higher rewards. Typically, the actor loss decreases over the course of training as the actor becomes better at selecting actions.\\
In the early episodes of training, the actor loss is high as the actor explores the environment and tries out different actions. As training progresses, the actor becomes more confident in its actions, and the loss decreases. If the actor loss does not decrease over the course of training, it indicates a problem with the training process or the environment itself. In such cases, it may be necessary to adjust the hyperparameters or try different training techniques to improve performance.\\

\subsubsection{Critic loss}\\
The \textit{critic loss vs episode graph} shows the loss of the critic changing over the course of training. The critic loss is a measure of how well the critic can estimate the value of the current state. Critic loss decreases over the course of training as the critic becomes better at estimating the state value.

In the early episodes of training, the critic loss may be high but as it progresses, the critic becomes more confident in its estimates, and the loss decreases. If the critic loss does not decrease over the course of training, it indicates a problem with the training process or the environment itself. In such cases, it may be necessary to adjust the hyperparameters or try different training techniques to improve performance.\\

\subsubsection{Level}\\
The \textit{level vs episode graph} shows how the agent's performance on different levels or stages of the environment changes over the course of training. This graph is particularly useful when training the agent on environments with different levels or stages, such as video games with multiple levels. Each point on the graph represents the agent's performance on a particular level or stage during a specific episode of the training process. The performance can be measured by different metrics such as cumulative reward, time taken to complete the level, or accuracy.\\
This graph can provide valuable insights into how the agent is progressing through the levels or stages of the environment. Ideally, the graph should show a steady increase in performance on each level over the course of training. If the agent is struggling on certain levels or stages, this can be identified by a plateau or a decline in performance on the corresponding levels.\\
The shape of the graph can vary depending on the specific environment and hyperparameters used for training. In general, the graph should show a positive trend in performance over time. However, there may be some variability in performance on individual levels or stages, which can be influenced by factors such as the level's difficulty, the randomness of the environment, or the agent's exploration strategy.\\
